---
title: "Decisions"
author: "Anouk Bouma"
format: html
editor: visual
---

This script is used only for the first stage of the project where the interrater reliability is calculated to evaluate how well the selection protocol works. For the later phases, where coding is done by only one reviewer per article, this script is not used.

## Loading decisions

```{r}
library(psych)
library(dplyr)
library(readxl)

e1 <- readRDS("C://101-200(reviewer1).rds")

e2 <- readRDS("C://101-200(reviewer2).rds")


# Creating a function to calculate IRR and list inconclusive papers
irr <- function(evaluator_data_1, evaluator_data_2) {
  
  # create decision variable that notes the decisions per paper for evaluator 1
  evaluator_data_1 <- evaluator_data_1 %>%
  mutate(decision = case_when(
    .[['included']] == TRUE ~ 1,
    .[['excluded']] == TRUE ~ 0,
    .[['second_reviewer']] == TRUE ~ 2,
    TRUE ~ NA_real_
  ))

  # create decision variable that notes the decisions per paper for evaluator 2
  evaluator_data_2 <- evaluator_data_2 %>%
    mutate(decision = case_when(
      .[['included']] == TRUE ~ 1,
      .[['excluded']] == TRUE ~ 0,
      .[['second_reviewer']] == TRUE ~ 2,
      TRUE ~ NA_real_
    ))

# counter variables to count how many conclusive and inconclusive choices are made
same <- 0
different <- 0

# loop over all papers and check for each one if the choice of e1 and e2 are the same
  for (i in 1:100) {
    if (evaluator_data_1[i,'included'] == evaluator_data_2[i, 'included'] & evaluator_data_1[i,'excluded'] == evaluator_data_2[i,'excluded'] & evaluator_data_1[i,'second_reviewer'] == evaluator_data_2[i,'second_reviewer']) {
      same <- same + 1
    } else { # if not the same, print the title of the paper and the decisions
      print(paste0(evaluator_data_1$title[i], 
        ". INCONCLUSIVE. ", 
        "evaluator_data_1: ", evaluator_data_1$decision[i], 
        " evaluator_data_2: ", evaluator_data_2$decision[i], 
        " note evaluator_1: ", evaluator_data_1$note[i], 
        " note evaluator_2: ", evaluator_data_2$note[i]))
      
      different <- different + 1
    }
}

# counter variables to count how many papers are included, excluded, or need to be reviewed
included <- 0
excluded <- 0
reviewer <- 0

# loop over all papers to count the number of included/excluded/reviewer papers
for (i in 1:100) {
  if (evaluator_data_1[i, 'included'] == TRUE & evaluator_data_2[i, 'included'] == TRUE) {
    included <- included + 1
  } else if (evaluator_data_1[i, 'excluded'] == TRUE & evaluator_data_2[i, 'excluded'] == TRUE) {
    excluded <- excluded + 1
  } else if (evaluator_data_1[i, 'second_reviewer'] == TRUE & evaluator_data_2[i, 'second_reviewer'] == TRUE) {
    reviewer <- reviewer + 1
  } 
}

# table of the decisions
print(table(evaluator_data_1$decision, evaluator_data_2$decision))

# calculate cohens kappa
cohen.kappa(x=cbind(evaluator_data_1$decision, evaluator_data_2$decision))
}

# running the function
irr(e1, e2)
```

## Excel file of the disagreements

```{r}
disagree <- function(evaluator_data_1, evaluator_data_2) {
  library(dplyr)

  # Create decision variables
  evaluator_data_1 <- evaluator_data_1 %>%
    mutate(decision = case_when(
      included == TRUE ~ 1,
      excluded == TRUE ~ 0,
      second_reviewer == TRUE ~ 2,
      TRUE ~ NA_real_
    ))

  evaluator_data_2 <- evaluator_data_2 %>%
    mutate(decision = case_when(
      included == TRUE ~ 1,
      excluded == TRUE ~ 0,
      second_reviewer == TRUE ~ 2,
      TRUE ~ NA_real_
    ))

  # Create a dataframe to store disagreements
  disagreements_df <- data.frame(
    index = integer(),
    title = character(),
    decision_e1 = numeric(),
    decision_e2 = numeric(),
    note_e1 = character(),
    note_e2 = character(),
    stringsAsFactors = FALSE
  )

  # Loop over all rows and collect disagreements
  for (i in 1:nrow(evaluator_data_1)) {
    same_decision <- evaluator_data_1[i, c("included", "excluded", "second_reviewer")] ==
                     evaluator_data_2[i, c("included", "excluded", "second_reviewer")]

    if (!all(same_decision, na.rm = TRUE)) {
      disagreements_df <- rbind(disagreements_df, data.frame(
        index = i,
        title = evaluator_data_1$title[i],
        decision_e1 = evaluator_data_1$decision[i],
        decision_e2 = evaluator_data_2$decision[i],
        note_e1 = evaluator_data_1$note[i],
        note_e2 = evaluator_data_2$note[i],
        stringsAsFactors = FALSE
      ))
    }
  }

  return(disagreements_df)
}
disagreements <- disagree(e1, e2)
#write.csv(disagreements, file = "disagreements.csv", row.names = FALSE)
```

Combining the results.

```{r}
# The result will be a dataframe as a copy of e1
resolved1 <- e1

for (article in 1:nrow(e1)) {
  if (e1[article,]$included == e2[article,]$included &&
      e1[article,]$excluded == e2[article,]$excluded &&
      e1[article,]$second_reviewer != TRUE && 
      e2[article,]$second_reviewer != TRUE) 
    { next }
     else {
        resolved1[article, c("included", "excluded", "second_reviewer")] <- FALSE
      }
}

new_review1 <- filter(resolved1, included == FALSE & excluded == FALSE | second_reviewer == TRUE)

# Van beide groepen de artikelen die opnieuw beoordeeld moeten worden combineren
review_combined <- rbind(new_review, new_review1)

saveRDS(review_combined, file = "disagreements_for_review.rds")
```

This object can be used in the shiny app to fill out the empty spaces, then the object can be added to the all_articles file
